Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-10-31 Response.tex

% !Mode:: "TeX:UTF-8"
\documentclass{article}
\author{Shengkai Chen}
\date{\today}
\title{Response to Reviewers' Comments}
\begin{document}
\maketitle

We would like to thank the Editor and reviewers for their insightful comments and suggestions. The issues raised by the reviewers have been addressed and a detailed response are given below.

\setlength\parindent{0pt}

\section*{Reviewer 1's comment}
I think that the initial background information given in the introduction could be explained a little bit better on simpler terms.

\textbf{Response:}

\subsection*{Comment 1} % (fold)
The literature review was good but could cover a little more. Additionally, the conclusion section seemed a little bit too short. It was dense but did not cover enough. Results section was good.

\textbf{Response:}

\subsection*{Comment 2} % (fold)
There are several issues of tense I found throughout the paper as well as grammar issues, especially in the terms section.

\textbf{Response:}

I'm so sorry to make such mistakes, related modifications have been made in new manuscript. Thank you.

\subsection*{Comment 3} % (fold)
One issue that I would address is that the figures such as figures one and two are not clear enough.  They need to be more crisp instead of blurry. The plots and graphs seem to be good on the other hand.

\textbf{Response:}

Thank you for the suggestion. I've changed the Fig. 1 into parallel style that enlarges the words in this figure, I've also redrawn Fig. 2 and Fig. 1 with \textit{MS Visio} so that they are more crisp now. 
\section*{Review 2's comment} % (fold)  
The authors should get in touch with the study's relevance with the environmental issues. Otherwise, the article's relevance with the conference is regarded to be low.
I would recommend the authors to describe the 3 modes (incubation, outsourcing, and metabolism modes) so that the readers can understand them more easily.

\textbf{Response:}

\end{document}

### 2016-10-31 intro.tex
add response

% !TEX root = Eco-Model.tex
\section{Introduction}
The relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information. Demanders prefer high quality of performance, while providers prefer high use rate of resource. A cloud platform operator prefers a suitable amount of registered resources to satisfy the needs of the market and for an easier life cycle management of resources. These preferences stimulate the emergence of good service pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem. Hence, it's important to identify a suitable operation mode to meet most of individuals' preference and to optimize the resource management.

>>>>

% !TEX root = Eco-Model.tex
\section{Introduction}
(use a bit simpler terms)

The relationship among entities in a cloud manufacturing system become more complicated than that in existing manufacturing systems, since the integration of advanced technologies makes it possible for individual to make decisions depend on enriched information. Demanders prefer high quality of performance, while providers prefer high use rate of resource. A cloud platform operator prefers a suitable amount of registered resources to satisfy the needs of the market and for an easier life cycle management of resources. These preferences stimulate the emergence of good service pattern that will lead to the emergence operation mode in the cloud manufacturing ecosystem. Hence, it's important to identify a suitable operation mode to meet most of individuals' preference and to optimize the resource management.
